\documentclass[11pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}

\geometry{margin=0.75in}
\setlength{\parindent}{0pt}
\pagestyle{empty}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{1ex}{0.5ex}

\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=black,
  pdfauthor={David Rosson},
  pdftitle={David Rosson -- Resume}
}

\begin{document}

\begin{center}
  {\LARGE \textbf{David Rosson}}\\[0.4em]
  \href{mailto:david@rosson.au}{david@rosson.au} \quad $|$ \quad
  +49\,163\,683\,1885 \quad $|$ \quad
  \href{https://linkedin.com/in/gartenfeld}{linkedin.com/in/gartenfeld} \quad $|$ \quad
  \href{https://medium.com/suomesta}{medium.com/suomesta}
\end{center}
\vspace{0.5em}

\section{Summary}

\begin{itemize}[leftmargin=*,nosep]
  \item Well-versed in JavaScript and frontend technologies. Top 10\% in Algorithms on HackerRank.
  \item Experienced in UI development and the engineering process of large-scale enterprise products.
  \item Familiar with architecture considerations for scalability, security, and robustness in a complex system.
  \item Emphasis on tooling, automation, workflow, quality through tests, maintainability, and iteration cycles.
  \item Strong proponent of rapid prototyping and evidence-driven design focused on real-world user experience.
\end{itemize}

\section{Experience}

\textbf{Senior Frontend Engineer --- Platform Engineering} \hfill 2022--2023 \\
\textit{Vivy GmbH}
\begin{itemize}[leftmargin=*,nosep]
  \item Solved technical issues to get teams unstuck, improved dev infrastructure and knowledge sharing.
  \item Oversaw migration of product features from end to end, managed engineering requirements.
\end{itemize}

\vspace{0.3em}
\textbf{Senior Software Engineer --- Design Systems Engineering} \hfill 2021 \\
\textit{ResearchGate GmbH}
\begin{itemize}[leftmargin=*,nosep]
  \item Collaborated with Design leadership and the Frontend Core team to modernise the design system.
  \item Empowered product (end user-facing) designers and engineers to experiment and develop at scale.
\end{itemize}

\vspace{0.3em}
\textbf{Frontend Engineer --- Automation UI and Business Insight} \hfill 2019--2021 \\
\textit{Ultimate.ai GmbH}
\begin{itemize}[leftmargin=*,nosep]
  \item Delivered a range of major features of significant business impact as the sole FE engineer on each project.
  \item Coordinated with product owners, designers and other tech teams to realise novel engineering designs.
  \item Performed extensive code reviews and made improvements to quality and maintainability of the code base.
  \item Experimented with visualisation and product features to rapidly respond to customer business cases.
  \item Promoted a culture of maintainable, reusable code and modernised scalable development practices.
\end{itemize}

\vspace{0.3em}
\textbf{Software Engineer --- UI and Data Visualisation} \hfill 2015--2017 \\
\textit{Cloudera, Inc. (NYSE:CLDR)}
\begin{itemize}[leftmargin=*,nosep]
  \item Introduced improvements in build automation and dependency management in legacy code base.
  \item Implemented modular UI components with data bindings that are reusable across products.
  \item Evangelised for frontend technologies and practices to encourage code sharing amongst teams.
  \item Enhanced the ease-of-use for specialised admin tools in the distributed computing ecosystem.
  \item Extended Analytics to collect data on usage patterns to inform user experience design.
\end{itemize}

\section{Education}

\textbf{Master of Science, ICT Innovation} \hfill \\
\textit{Technische Universit채t Berlin}, Fakult채t IV Informatik

\vspace{0.2em}
\textbf{Master of Science (Technology), Human-Computer Interaction and Design} \hfill \\
\textit{Aalto University}

\vspace{0.2em}
\textbf{Bachelor of Science (Linguistics)}; Exchange: Uni.\ Jyv채skyl채 (Psych) \hfill \\
\textit{Macquarie University}

\section{Keywords}

JavaScript, TypeScript, Babel, Webpack, npm, yarn, React, Redux, Next.js, Jest, Jasmine, Mocha, End-to-End Testing, Puppeteer, Git, HTML\,5, CSS\,3, LESS, JSS, Material UI, Styled Components, Storybook, D3, Recharts, react-vis, Object-Oriented and Functional JS, Promises/A+, Async/Await, Build Automation, Node.js, Express, REST, API Integration, Relational Databases, MySQL, MongoDB, GraphQL, TCP/HTTP, Chrome DevTools, Code review, JIRA, Agile, Scrum, Kanban, Bash scripting, Python, Web scraping, Google Analytics.

\end{document}
